Turbulence in compact to giant H~II regions

### 2023-04-23 strucfunc_paper.tex
Finish section on 30 Dor

\citet{Melnick:2021x} also investigated the structure function in 30~Doradus finding that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
This does not agree with our results, since we establish the existence of correlations up to the maximum value of the structure function that occurs at \SI{20}{pc}, separation where a value of 2\(\sigma\pos^2\) is reached.
The VLT FLAMES/GIRAFFE observations of \citet{Melnick:2021x} may not have had the resolution to resolve the correlations at small separations, however an inspection of its velocity map (figure 7 in their work) shows that the velocity distribution is not completely random.
\citet{Melnick:2021x} \(\sigma\pos\) values range from \num{11.6} to \SI{18.2}{km.s^{-1}} for a diverse type of fits (see figure~15 on their paper).
The first attempt at characterizing turbulence in a giant extragalactic \hii{} region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between spatial scales of \num{10} and \SI{100}{pc}.
The \citet{1961MNRAS.122....1F} is in broad agreement with the \citet{Melnick:2021x} results in which they consider profiles classified as singles.
The large scales of our structure function falls between the two previous results.
The previous happens at \SI{5}{pc} and \SI{40}{pc} (which covers small-to-intermediate scale for previous investigations and large scales for us) and for \(B(r)\) between \num{250} to \SI{600}{km^{2}.s^{-2}} where our results show a downward 'hook' pattern.

>>>>

\citet{1961MNRAS.122....1F} investigated the structure function in 30~Doradus by using
spectra at \(N = 37\) different points, spread over a region of diameter \SI{150}{pc}
and with minimum separation of \SI{4}{pc}.
Velocities were measured by combining results from multiple spectral lines in
the blue spectral region, the strongest being of [\ion{O}{2}], [\ion{O}{3}], and \hb{}.
They found an essentially flat \(B(r)\) for \(r > \SI{10}{pc}\) with
\(\sigma\pos^2 = \SI{130}{km.s^{-1}}\), which is roughly half the value that we determine for the
central region of the nebula (of diameter \SI{30}{pc}).
This implies that the amplitude of the fluctuations is falling with radius,
similar to what we inferred above for the Orion Nebula.
For the smallest separations, of order \SI{4}{pc}, they found that \(B(r)\) declined
significantly, although an exact measurement was hampered by uncertainties in the
correction for the effects of noise.
This behavior is consistent with our own value of \(r_0 = \SI{4}{pc}\),
suggesting that the correlation length is not greatly different
in the wider area covered by their study.
This is a clear difference from the Orion Nebula,
where we find a significantly larger correlation length
in the extended nebula than in the core.

\citet{Melnick:1987a} used Fabry-Perot observations in \ha{} and [\ion{O}{3}]
from \citet{Smith:1972a} to calculate
the structure function over a region of diameter \SI{50}{pc},
which is smaller than in \citet{1961MNRAS.122....1F}
but with a slightly larger number of spatial samples (\(N = 44\)).
They found an approximately flat \(B(r)\) for \(r > \SI{20}{pc}\)
and a shallow rising power law, \(\text{index} \approx 0.16\), for \(r = 5\) to \SI{20}{pc},
with \(\sigma\pos^2 \approx \SI{280}{km.s^{-1}}\).
This is similar to our own results over the same range of separations,
including the local peak in \(B(r)\) at \(r = \SI{20}{pc}\),
which is clearly visible in Figure~A2 of \citet{Melnick:1987a}.
The reason that \citeauthor{Melnick:1987a} measure such a shallow slope for their smallest
separations is that they are only sampling the range from \(1.25 r_0 \to 5 r_0\),
in which the structure function is tending toward its asymptotic value of \(2 \sigma\pos^2\).
In order to measure the power-law portion of the structure function,
it would be necessary to sample separations as small as \SI{1}{pc} or \SI{4}{arcsec}.

\citet{Melnick:2021x} used \ha{} spectra from VLT FLAMES/GIRAFFE (see section~\ref{sec:flames-multi-fiber}) for \(N = 1668\) distinct fiber positions
covering a region of diameter \SI{300}{pc}
\citep{Torres-Flores:2013t}.
They claim to find a completely flat structure function on scales from \num{3} to \SI{200}{pc},
which seriously conflicts with our own observations at the lower end of this range.
In particular, their two smallest separation bins are centered on \(r = 2.5\) and \SI{7.5}{pc},
for which our own results yield \(B(r) / \sigma\los^2 \approx 0.7\) and \(1.3\),
respectively (our Figure~\ref{fig:strucfunc-fit-MC}a),
whereas they find \(B(r) / \sigma\los^2 \approx 2.0\) at all separations (see their Figure 15).
We are at a loss to explain this discrepancy, which is inconsistent not only with our own results,
but also with those of \citet{1961MNRAS.122....1F} and \citet{Melnick:1987a},
who both found at least some evidence for a downturn in \(B(r)\) for \(r < \SI{10}{pc}\). 
The result also seems to contradict the evidence of their own Figures~7 and~13,
which show spatial coherence in the velocity field.
If the structure function were truly flat, then blue shifted and red shifted profiles
would be randomly mixed spatially, which is not observed.
